% !TeX root = ../main.tex

\begin{publications}

\section*{已发表论文}

\begin{enumerate}
    \item {\textbf{Xiao-Kang Sun}, Gongfa Liu. et.al., The prototype of equipment protection system based on Ethernet POWERLINK for HALS[J]. Nuclear Inst. and Methods in Physics Research, A, 2019, 946}
    \item{\textbf{X.K. Sun}, Yifan Song, G. Liu, Distributed I/O System Based on Ethernet POWERLINK Under the EPICS Architecture,Vancouver, British Columbia, Canada, 2018}
    \item \textbf{孙晓康},宋一凡,李川,蒋思远,刘功发.HLS-II恒温冷却水控制系统的设计与实现[J].原子能科学技术,2018,52(06):1139-1143.
    \item {Shuang Xu, \textbf{Xiaokang Sun}, et.al., Control system design for front end devices of IRFEL, Proceedings of IPAC2018, Vancouver, British Columbia, Canada, 2018}
    \item {Zi-yu Huang, \textbf{X.K. Sun}, G. Liu, EPICS Driver for Siemens CP1616 Communication Module, IPAC2018, Vancouver, BC, Canada, 2018}
    \item {Z.X. Shao, \textbf{X.K. Sun}, et.al., Research and design of digital magnet power supply controller for HALS, IPAC2019, Melbourne, Australia, 2019}
\end{enumerate}

% \section*{待发表论文}

% \begin{enumerate}

% \end{enumerate}

\section*{专利}
\begin{enumerate}
\item 孙晓康，李川，宣科，王季刚，刘功发. 一种用于大科学装置设备联锁保护方法及系统. 公开号：CN110191181A.
\end{enumerate}

\section*{软件著作权}
\begin{enumerate}
\item 孙晓康；刘功发；宣科；李川；唐雷雷；王季刚. 千兆POWERLINK通信软件. 登记号: 2020SR083872.
\end{enumerate}

\section*{博士期间参与的科研项目}
\begin{enumerate}
    \item 国家自然科学基金面上项目“用于EPICS输入输出控制器的冗余技术研究”（编号：11375186）
    
    \item 合肥先进光源预研工程“加速器控制技术研究” 子项目
\end{enumerate}

\end{publications}
